Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex
Update

At a high level, we are interested in understanding whether \sys can indeed scale pipelines out automatically and correctly.
To achieve this, we use a combination of micro-benchmarks and one macro-benchmark, most of which were collected from prior literature and online repositories.
Micro-benchmarks~\sx{micro} are one-off, simple one-line pipelines that take a few seconds to write;
  such pipelines are usually composed interactively to solve a task at hand, test a hypothesis, or ``smoke out bugs''~\cite{bentley1986literate}---but, with \sys, applied to very large data sets.
These pipelines are taken from real use cases (often from the literature~\cite{bentley1985spelling}), and, precisely due to their small size, have the benefit of highlighting stress on a handful of stages.

@@

\kk{exoume ena semantic model to opoio mporei na xrhsimopoiithei gia
  na ginoun formally proven claims gia to equivalence preservation twn
  optimizations etc.}

>>>>

At a high level, we are interested in understanding whether \sys can indeed scale pipelines out automatically and correctly.
To achieve this, we use a combination of micro-benchmarks and one macro-benchmark, most of which were collected from prior literature and online repositories.
Micro-bench\-marks~\sx{micro} are one-off, simple one-line pipelines that take a few seconds to write;
  such pipelines are usually composed interactively to solve a task at hand, test a hypothesis, or ``smoke out bugs''~\cite{bentley1986literate}---but, with \sys, applied to very large data sets.
These pipelines are taken from real use cases (often from the literature~\cite{bentley1985spelling}), and, precisely due to their small size, have the benefit of highlighting stress on a handful of stages.

@@

% \kk{exoume ena semantic model to opoio mporei na xrhsimopoiithei gia
%   na ginoun formally proven claims gia to equivalence preservation twn
%   optimizations etc.}
